Rank verification for exponential families

### 2016-04-08 verifying-winner.tex
Gupta and Nagel now does X* - X1 instead of X* - X**

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(N, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $N$ and $n$. The two procedure coincide if $n = 2$ as there are is actual selection. However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

>>>>

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(N, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $N$ and $n$. The procedure by Gupta and Nagel coincides with our procedure at $n = 2$ if we half our $\alpha$. However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test even for the same $\alpha$.
